Extracting Menu Navigation and Program Configuration Events from User Interface Video Tutorials

### 2015-04-20 paper/main.tex
Paper: added citations in BibTeX

@@

Video tutorials have become prevalent for learning software (Matejka et al. 2011, 
Pongnumkul et al. 2010, 1).  Banovic et al. claim this may be because users 
can directly observe expert use, which can serve as a strong learning aid 
(Shneiderman 1983, (1, 4)).  Grossman \& Fitzmaurice showed benefits of short 
contextual video clips (Grossman \& Fitzmaurice 2010, 1).  Short, 10-25 second 
contextually available videos were effective to help users accomplish task and 
retain what they learned than traditional text-based tutorials (Grossman \& 
Fitzmaurice 2010, 4).

Though they also have their drawbacks (Hategekimana et al. 2008, 4):  
Navigation issues could lead to misunderstanding of content (Harrison 1995, 
(1, 4)), and users may not be able to keep up with the pace of the content 
(Palmiter \& Elkerton 1991, 1).  Researchers working with longer, 2-3 minute 
task-oriented tutorials found that users performed better with text tutorials 
than videos because users could not work at the same pace as the video 
(Grabler et al. 2009, 4).  Almost all research on instructional videos point 
to a need for segmented videos that emphasize each step of the task (4).

@@

\textbf{Andrew: This should all use citations, not parentheses.}

\subsection{Reverse Engineering UIs}

Runtime modification of existing interfaces is one application of reverse 
engineeing UIs.  For example, replacing the toolkit drawing object and 
intercepting commands (Edwards et al. 1997, Olsen et al. 1999, 2).  Others 
have used interface introspection using the accessibility API 
(Stuerzlinger et al. 2006, 2).  Others have dynamically loaded code into 
the program space, for example with Scotty (Eagan et al. 2011, 2).

Sikuli (Yeh et al. 2009, 1) uses computer vision to identify GUI elements from 
screen captures, using template matching and voting based on invariant local 
features (Yeh et al. 2009, 2).  Sikuli also searches for UI elements in the 
interface (Bergman et al. 2005, 1), and automates GUI tasks (Chang et al. 2010, 
1).  For searching based on screenshots, 3 types of features are extracted: 
text from the source document, visual words computed from visual words from 
MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
text extracted through OCR (4).  For searching on the screen for saved 
screenshot images, small patterns are found via template matching and large 
patterns through invariant feature voting (4).

Pause-and-Play extends the template matching approach of Sikuli to detect 
tool-selection UI events in compressed, low-resolution video tutorials.  
The system takes a tool palette template and tool icons as input, 
producing metadata file of tool changes with timecodes.  With template 
matching at multiple resolutions, detection is invariant to recording 
resolution and some camera effects.  Their system cannot be run in in 
real-time (3).

A number of different technologies attempt to learn templates for UI 
elements (Chang et al. 2011, Dixon \& Fogarty 2010, Hurst et al. 2010, 
Matejka et al. 2011, 1), using information from mouse APIs (Hurst et al. 
2010, 1) and accessibility APIs (Chang et al. 2011).  Prefab identifies GUI 
elements with GUI specific visual features (Dixon \& Fogarty 2010, 1), which 
enables overlay of advanced interactions on existing interfaces (Dixon et al. 
2011, Dixon et al. 2012, 1).  Waken contributes to this space by discovering 
cursor shapes, clicking actions, icons, tooltips and menus, all by examining 
the difference between frames of UI video.  They do this by making assumptions 
about how the image of icons change during hover and press actions.  Detection 
of the cursor and icons in later frames is performed by template matching (1).

Pixel-based methods for reverse engineering UIs are motivated by their 
indepenedece from underlying application or toolkit requirements (2).  Work 
by Zettleymoyer et al. (Zettlemoyer et al. 1998, Zettlmoyer et al. 1999, 2) 
examine widget identification in IBOTS and VisMap and in programming by 
example (St. Amant et al., Potter, St. Amant et al. 2005, 2).  Olsen et al.'s 
ScreenCrayons links ink annotations to arbitrary screen elements (Olsen et al. 
2004, 2), and Tan et al.'s work interactively subdivides windows with a 
copy-paste metaphor (Tan et al. 2004, 2).

To delve into the technical implementations of the Prefab pixel-based 
matching algorithm, we report from (2).  Prefab identifies interface elements 
with a library of prototypes.  This uses two strategies: exact matches of 
prototype pixels against an image, and modelining the prototype background 
and differencing pixel in an image to identify foreground interface elements.  
Prefab generalizes from example images to models which contain parts like 
exact pixel features, or regions or areas of variable size or repeating 
patterns.  It organizes the entire interface into a hierarchy (2).

>>>>

Recent research has focused on how to improve the use of video tutorials 
to help users learn software ~\cite{matejka_ambient_2011}~\cite{pongnumkul_pause-and-play_2011}.  
One strength of video tutorials may be that users
can directly observe expert use, which can serve as a strong learning aid~\cite{shneiderman_direct_1983}.  Grossman \& Fitzmaurice showed benefits of short 
contextual video clips.  Short, 10-25 second 
contextually available videos were effective to help users accomplish task and 
retain what they learned than traditional text-based tutorials~\cite{grossman_toolclips_2010}.

However, video tutorials have drawbacks:
Navigation issues could lead to misunderstanding of content~\cite{harrison_comparison_1995}.
Users may not be able to keep up with the pace of the content~\cite{palmiter_evaluation_1991}.
Researchers working with longer, 2-3 minute 
task-oriented tutorials found that users performed better with text tutorials 
than videos because users could not work at the same pace as the video~\cite{grabler_generating_2009}.
In general, research on instructional videos point shows a need to segmented videos to
emphasize the steps of the task.

@@

@@

\subsection{Visually Reverse Engineering UIs}

By examining pixels, many have succeeded at reverse engineering user interfaces
and interactions with user interfaces with purely visual information, independent
of any knowledge of underlying application implementation. Work 
by Zettleymoyer et al.~\cite{zettlemoyer_ibots_1999}~\cite{zettlemoyer_visual_1999}
examine widget identification in IBOTS and VisMap.  Also see~\cite{potter_triggers_1992}~\cite{amant_image_2005}~\cite{lieberman_visual_2001}. 
Visual identification of widgets and UIs may also have also been used in Olsen 
et al.'s ScreenCrayons work that links annotations to arbitrary screen 
elements~\cite{olsen_jr_implementing_1999},
and in Tan et al.'s work to interactively subdivide windows with a 
copy-paste metaphor~\cite{tan_wincuts_2004}.
\textbf{Andrew: Check on this.}

More recently, Sikuli~\cite{yeh_sikuli_2009} uses computer vision to 
identify GUI elements from screen captures, using template matching for small
UI elements and voting based on invariant local features for large elements.
In application, Sikuli allows users to search for documentation related to
screenshots taken of UI elements, and to script GUI tasks using visual
cues of the UI.  For searching based on screenshots, 3 types of features are 
extracted: text from the source document, visual words computed from visual 
words from MSER-detected salient elliptical patches, and 3-grams over widget-embedded 
text extracted through OCR.  For searching on the screen for saved 
screenshot images, small patterns are found via template matching and large 
patterns through invariant feature voting.

Pause-and-Play extends the template matching approach of Sikuli to detect 
tool-selection UI events in compressed, low-resolution video tutorials.  
The system takes a tool palette template and tool icons as input, 
producing metadata file of tool changes with timecodes.  With template 
matching at multiple resolutions, detection is invariant to recording 
resolution and some camera effects.  Their system cannot be run in in 
real-time~\cite{pongnumkul_pause-and-play_2011}.

A number of different technologies attempt to learn templates for arbitrary UI 
elements~\cite{chang_associating_2011}~\cite{dixon_prefab_2010}~\cite{hurst_automatically_2010}~\cite{matejka_ambient_2011}.
Learning may require access to mouse APIs~\cite{hurst_automatically_2010}
and accessibility APIs~\cite{chang_associating_2011}.

Prefab identifies GUI elements with GUI specific visual features~\cite{dixon_prefab_2010}, which 
enables overlay of advanced interactions on existing interfaces~\cite{dixon_content_2011}~\cite{dixon_general-purpose_2012}.
\textbf{Andrew: Check up on this initial description.  I'm also not sure
if Prefab actually belongs in this conceptual group.}
To delve into the technical implementations of the Prefab pixel-based 
matching algorithm, we report from~\cite{dixon_general-purpose_2012}.
Prefab identifies interface elements using a library of prototypes.  
This uses two strategies: exact matches of prototype pixels against an image,
and modelining the prototype background and differencing pixel in an image 
to identify foreground interface elements.  
Prefab generalizes from example images to models which contain parts like 
exact pixel features, or regions or areas of variable size or repeating 
patterns.  It organizes the entire interface into a hierarchy.

Waken contributes to this space by discovering 
cursor shapes, clicking actions, icons, tooltips and menus, all by examining 
the difference between frames of UI video.  They do this by making assumptions 
about how the image of icons change during hover and press actions.  Detection 
of the cursor and icons in later frames is performed by template matching~\cite{banovic_waken_2012}.
We rely on techniques similar to those in Waken to establish when menus
have been activated and menu items selected.
